---
title: "Customer Segmentation"
author: "Chekeb Panschiri"
date: "10/11/2021"
output:
  html_document:
    df_print: paged
    theme: flatly
  pdf_document: default
params:
  interactive: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    fig.align = "center")
```

```{r}
library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel)
library(plotly)
```

```{r}
bike_orderlines_tbl <- read_rds("Data/bike_orderlines.rds")
```

```{r}

  source("func.R")
```


## Dataset

The dataset used for this little project is consisting of bike sales orders from a bike manufacturer to different shops in the US. We will use this data to see the customers' preferences towards the different bike models in general and by segments.

We first visualize 

<!-- ## Solution Summary -->
<!-- The data science team has identified 4 customer segments. The 4 customer segments were given descriptions based on the customer's top product purchases. -->

<!-- 1. __Segment 1 Preferences:__ Mountain Bikes, Above $3200 (Premium Models) -->
<!-- 2. __Segment 2 Preferences:__ Road Bikes, Above $3200 (Premium Models) -->
<!-- 3. __Segment 3 Preferences:__ Road Bikes, Below $3200 (Economical Models) -->
<!-- 4. __Segment 4 Preferences:__ Both Roadn and Mountain, Below $3200 (Economical Models) -->

## Customer Preferences

### Heat Map

Our customer-base consists of 30 bike shops. Several customers have purchasing preferences for Road or Mountain Bikes based on the proportion purchased by sub-categories.

```{r, fig.height=12}
# PLOT CUSTOMER HEAT MAP
plot_customer_heatmap(interactive = params$interactive)
```

### Customer Segmentation

This is a 2D projection bases on customer similarity that exposes 4 clusters, which are key segments in the customer base. 

```{r, fig.height=5, fig.width=7}
# PLOT CUSTOMER SEGMENTS
plot_customer_segments(k = 4, seed = 123, interactive = params$interactive)
```


### Customer Preferences By Segment

1. __Segment 1 Preferences:__ Mountain Bikes, Above $3200 (Premium Models)
2. __Segment 2 Preferences:__ Road Bikes, Above $3200 (Premium Models)
3. __Segment 3 Preferences:__ Road Bikes, Below $3200 (Economical Models)
4. __Segment 4 Preferences:__ Both Road and Mountain, Below $3200 (Economical Models)

```{r, fig.height=8}
# PLOT CUSTOMER BEHAVIOR
plot_customer_behavior_by_cluster(top_n_products = 20, k = 4 , seed = 123, interactive = params$interactive)
```

